Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
adding a section on incrementality

>>>>

\subsection{Incrementality}
\label{sec:incrementality}

The design of \sysname guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor. We experimentally confirmed that our implementation provides this guarantee. To the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing the prefix that a router originates. In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed. In contrast, all router configurations were modified with Propane because it heavily uses prefix lists which are sensitive to such changes. While Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.
